Engineering the Servo Web Browser Engine using Rust

### 2015-10-23 icse16-servo/browsers.tex
Edit intro to browsers section, move some to paper intro.
The browser section is all about architecture. The first sentence
about how its used is out of place.

Modern web browsers do not just load static pages, but can also handle pages that have similar
complexity to native applications.
From application suites such as the Google Apps\footnote{\url{https://apps.google.com}} to games
based on the Unreal Engine,\footnote{\url{https://www.unrealengine.com/}}
modern browsers have the ability to handle much more than simple static pages.
\figref{fig:browser} shows the steps in processing a site.
While the naming is specific to the Servo browser, similar steps are used in all modern browsers.\footnote{\url{http://www.html5rocks.com/en/tutorials/internals/howbrowserswork/}}
\begin{figure*}[ht]
  \begin{center}
    \includegraphics[scale=0.55]{pics/browser}
  \end{center}%
  \caption{Processing stages and intermediate representations in a browser engine.}
  \label{fig:browser}
\end{figure*}%

>>>>

The architecture of all browsers are broadly the same, as demanded be the specifications of
the web platform and the shared history and wisdom of browsers and their authors.
As such, the steps Servo uses in \figref{fig:browser} to process a web page
are similar to those used in all modern browsers.\footnote{\url{http://www.html5rocks.com/en/tutorials/internals/howbrowserswork/}}
\begin{figure*}[ht]
  \begin{center}
    \includegraphics[scale=0.55]{pics/browser}
  \end{center}%
  \caption{Processing stages and intermediate representations in a browser engine.}
  \label{fig:browser}
\end{figure*}%
